---
title: "enrollment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

```{r}
d<-c(2,2,1,1,2,2,1,2,2,2,3,
     2,0,0,0,0,0,0,1,3,7,2)
data<-data.frame(matrix(d,2,11,byrow=TRUE),row.names = c("ALS","Control"))
colnames(data)<-seq(1,11,by=1)
```


#Function 1: Number of subjects(ALS and control) enrolled at x month - based on the real data 
```{r}
#number_of_subjects_enrolled_at_x
#get x
#add until you get x
nsubjects_ALS<- function(x) print(sum(data[1,c(1:x)],na.rm=T))
nsubjects_control<- function(x) print(sum(data[2,c(1:x)],na.rm=T))

```

#Function 2: Number of visits at x month - based on real data
```{r}
#number_of_visits
total_visit_ALS<-function(x)
{
#set<-ifelse(x>length(data),append(as.numeric(data[1,1:length(data)]),replicate(x-length(data),0)), as.numeric(data[1,1:x]))
#if_condition_to_calculate_future_number_of_visits_with_limited_subject_enrolled
if(x>length(data)) set<-append(as.numeric(data[1,1:length(data)]),replicate(x-length(data),0)) else set<-as.numeric(data[1,1:x])
c<-seq(x-1,0,by=-1)
d<-ifelse(c>=4|c==0,as.integer(c/4)+1,1)
#e_is_to_ensure_the_number_of_visits_doesn't_cross_5
e<-ifelse(d>=5,5,d)
total_vists=sum(set*e)

df=data.frame(visits=e,nos=set)

f<- df%>%
  group_by(visits)%>%
  summarise(totalnos=sum(nos))%>%
  mutate(plasma=22*visits*totalnos,serum=16*visits*totalnos,urine=11*visits*totalnos,
         csf_min=ifelse(visits<=2,0,visits-2), csf_max=ifelse(visits<=3,visits,3),
         csf_min_sample=32*totalnos*csf_min, csf_max_sample=32*totalnos*csf_max)

result<- data.frame(total_visits=total_vists,Plasma=sum(f$plasma),Serum=sum(f$serum),Urine=sum(f$urine),CSF_min=sum(f$csf_min_sample),CSF_max=sum(f$csf_max_sample))

return(list(f %>% select(visits,subjects=totalnos), result))

}
```

```{r}
total_visit_control<-function(x)
{
#set<-ifelse(x>length(data),append(as.numeric(data[1,1:length(data)]),replicate(x-length(data),0)), as.numeric(data[1,1:x]))
#if_condition_to_calculate_future_number_of_visits_with_limited_subject_enrolled
if(x>length(data)) set<-append(as.numeric(data[2,1:length(data)]),replicate(x-length(data),0)) else set<-as.numeric(data[2,1:x])
c<-seq(x-1,0,by=-1)
d<-ifelse(c>=6|c==0,as.integer(c/6)+1,1)
#e_is_to_ensure_the_number_of_visits_doesn't_cross_2
e<-ifelse(d>=2,2,d)
return(sum(set*e))
}
```


```{r}

```
dates = seq(as.Date("07-01-2021",  format = "%d-%m-%Y"), length.out = 120, by = "month")

#Function 3: Predicted model based on total number of subjects after 3 years
#Minimum annual enrollment - 50 for ALS and 20 for controls

```{r}
#getting_total_enrollments
#for (i in 1:11) d$sum[i]<-sum(d[c(1:i),1])
d <- as.data.frame(data %>% t())

for (i in 1:11) d$sum_ALS[i]<-nsubjects_ALS(i)
for (i in 1:11) d$sum_control[i]<-nsubjects_control(i)

d[12,]<-c(0,0,50,20)
d[24,]<-c(0,0,110,45)
d[36,]<-c(0,0,180,75)

d$time<-seq(1,36,1)
d$dates = seq(as.Date("01-07-2021",  format = "%d-%m-%Y"), length.out = 36, by = "month")
 
p <- d %>% 
  ggplot(aes(x=time,y=sum_ALS))+
  geom_point(aes(x=time,y=sum_ALS))+
  scale_x_continuous(breaks=c(1,2,3,4,5))+
  stat_smooth(method="gam",color="#69b3a2")
  scale_x_date(date_labels = "%b-%Y")


#model<- glm(sum_ALS~time,data=d)
model_ALS<- glm(sum_ALS~dates,data=d)
model_control<- glm(sum_control~dates,data=d)

```

#Predicts the total number of subjects at x month based on the model 

```{r}

newdata<- data.frame(dates=as.Date(c("2023-03-01","2023-07-01","2023-09-01","2024-02-01")))
                     
#newdata<- data.frame(time=c(26,30,34))
newdata<- data.frame(dates=seq(as.Date("01-07-2021",  format = "%d-%m-%Y"), length.out = 36, by = "month"))

ans<-data.frame(predicted_ALS=predict(model_ALS,newdata))
c_ans<-cbind(newdata,ans)

ans_c<-data.frame(predicted_control=predict(model_control,newdata))
d_ans<-cbind(c_ans,ans_c)
#d_ans$dates<-format(d_ans$dates,"%b %Y")
d_ans


```

```{r fig.height=8, fig.width=8}

stat_table<- d_ans %>%
  mutate(nos_month = floor(predicted_ALS - lag(predicted_ALS, default=first(predicted_ALS))),
         nos_month_c= floor(predicted_control - lag(predicted_control, default = first(predicted_control))))


data<-stat_table %>%
  dplyr::select(ALS=nos_month,Control=nos_month_c) %>%
  rownames_to_column() %>%
  pivot_longer(, cols = -rowname) %>%
  pivot_wider(, names_from = rowname) %>%
  as.data.frame()

rownames(data)<-data$name
data<-data[,-1]
# 
# total_visit_ALS(100)
# 
# total_visit_control(100)
# 
# 
# nsubjects_ALS(36)
# nsubjects_control(36)


final<-merge(stat_table,d,by="dates")

for (i in 1:36) final$output1[i]<-total_visit_ALS(i)[1]
for (i in 1:36) final$output2[i]<- total_visit_ALS(i)[2]

for (i in 1:36) final$tooltip[i] <- knitr::kable(final$output1[i], format = "html")
  
  fin<-final %>% 
  ggplot(aes(x=dates,y=predicted_ALS,tooltip=tooltip))+
  geom_point_interactive(aes(color="Predicted"))+
  geom_smooth_interactive(method="gam",color="#69b3a2",tooltip="")+
  scale_x_date(date_labels = "%b-%Y", date_breaks = "2 month")+
  geom_point(aes(x=dates,y=sum_ALS,color="Actual"))+
  geom_smooth(aes(x=dates,y=sum_ALS),method="gam")+
  theme(axis.text.x = element_text(angle=90,vjust=0.5),
              axis.title.y = element_text(vjust = 1,size=10),
              plot.title = element_text(hjust=0.5,color="darkred",size = 10,face = "bold"),
              legend.title = element_text(size=0),
              legend.text = element_text(size=6))+
  labs(title="Predicted subject enrollment from June 2021- June 2024", x="",y="No. of subjects(n)")


girafe(ggobj = fin,
       options= list(
         opts_tooltip(
           opacity = 0.8, use_fill = TRUE,
      use_stroke = FALSE, 
      css = "padding:5pt;font-family: Open Sans;color:white"),
      opts_hover_inv(css = "opacity:0.5"), 
      opts_hover(css = "fill:#4c6061;")
       ))


```

```{r}

for (i in 1:36) final$tooltip2[i] <- knitr::kable(final$output2[i], format = "html")
  
  fin<-final %>% 
  ggplot(aes(x=dates,y=predicted_ALS,tooltip=tooltip2))+
  geom_point_interactive(aes(color="Predicted"))+
  geom_smooth_interactive(method="gam",color="#69b3a2",tooltip="")+
  scale_x_date(date_labels = "%b-%Y", date_breaks = "2 month")+
  geom_point(aes(x=dates,y=sum_ALS,color="Actual"))+
  geom_smooth(aes(x=dates,y=sum_ALS),method="gam")+
  theme(axis.text.x = element_text(angle=90,vjust=0.5),
              axis.title.y = element_text(vjust = 1,size=10),
              plot.title = element_text(hjust=0.5,color="darkred",size = 10,face = "bold"),
              legend.title = element_text(size=0),
              legend.text = element_text(size=6))+
  labs(title="Predicted subject enrollment from June 2021- June 2024", x="",y="No. of subjects(n)")

girafe(ggobj = fin,
       options= list(
         opts_tooltip(
           opacity = 0.8, use_fill = TRUE,
      use_stroke = FALSE, 
      css = "padding:5pt;font-family: Open Sans;color:white"),
      opts_hover_inv(css = "opacity:0.5"), 
      opts_hover(css = "fill:#4c6061;")
       ))

```
