---
title: "enrollment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

```{r}
d<-c(2,2,1,1,2,2,1,2,2,2,3,
     2,0,0,0,0,0,0,1,3,7,2)
data<-data.frame(matrix(d,2,11,byrow=TRUE),row.names = c("ALS","Control"))
colnames(data)<-seq(1,11,by=1)
```


#Function 1: Number of subjects(ALS and control) enrolled at x month - based on the real data 
```{r}
#number_of_subjects_enrolled_at_x
#get x
#add until you get x
nsubjects_ALS<- function(x) print(sum(data[1,c(1:x)],na.rm=T))
nsubjects_control<- function(x) print(sum(data[2,c(1:x)],na.rm=T))

```

#Function 2: Number of visits at x month - based on real data
```{r}
#number_of_visits
total_visit_ALS<-function(x)
{
#set<-ifelse(x>length(data),append(as.numeric(data[1,1:length(data)]),replicate(x-length(data),0)), as.numeric(data[1,1:x]))
#if_condition_to_calculate_future_number_of_visits_with_limited_subject_enrolled
if(x>length(data)) set<-append(as.numeric(data[1,1:length(data)]),replicate(x-length(data),0)) else set<-as.numeric(data[1,1:x])
c<-seq(x-1,0,by=-1)
d<-ifelse(c>=4|c==0,as.integer(c/4)+1,1)
#e_is_to_ensure_the_number_of_visits_doesn't_cross_5
e<-ifelse(d>=5,5,d)
return(sum(set*e))
}
```

```{r}
total_visit_control<-function(x)
{
#set<-ifelse(x>length(data),append(as.numeric(data[1,1:length(data)]),replicate(x-length(data),0)), as.numeric(data[1,1:x]))
#if_condition_to_calculate_future_number_of_visits_with_limited_subject_enrolled
if(x>length(data)) set<-append(as.numeric(data[2,1:length(data)]),replicate(x-length(data),0)) else set<-as.numeric(data[2,1:x])
c<-seq(x-1,0,by=-1)
d<-ifelse(c>=6|c==0,as.integer(c/6)+1,1)
#e_is_to_ensure_the_number_of_visits_doesn't_cross_2
e<-ifelse(d>=2,2,d)
return(sum(set*e))
}
```


```{r}

```
dates = seq(as.Date("07-01-2021",  format = "%d-%m-%Y"), length.out = 120, by = "month")

#Function 3: Predicted model based on total number of subjects after 3 years
#Minimum annual enrollment - 50 for ALS and 20 for controls

```{r}
#getting_total_enrollments
#for (i in 1:11) d$sum[i]<-sum(d[c(1:i),1])
d <- as.data.frame(data %>% t())

for (i in 1:11) d$sum_ALS[i]<-nsubjects_ALS(i)
for (i in 1:11) d$sum_control[i]<-nsubjects_control(i)

d[12,]<-c(0,0,50,20)
d[24,]<-c(0,0,110,45)
d[36,]<-c(0,0,180,75)

d$time<-seq(1,36,1)
d$dates = seq(as.Date("01-07-2021",  format = "%d-%m-%Y"), length.out = 36, by = "month")
 
d %>% 
  ggplot(aes(x=dates,y=sum_ALS))+
  geom_point(aes(x=dates,y=sum_ALS))+
  stat_smooth(method="gam", color="#69b3a2")+
  scale_x_date(date_labels = "%b-%Y")

#model<- glm(sum_ALS~time,data=d)
model_ALS<- glm(sum_ALS~dates,data=d)
model_control<- glm(sum_control~dates,data=d)

```

#Predicts the total number of subjects at x month based on the model 

```{r}

newdata<- data.frame(dates=as.Date(c("2023-03-01","2023-07-01","2023-09-01","2024-02-01")))
                     
#newdata<- data.frame(time=c(26,30,34))


ans<-data.frame(predicted_ALS=predict(model_ALS,newdata))
c_ans<-cbind(newdata,ans)

ans_c<-data.frame(predicted_control=predict(model_control,newdata))
d_ans<-cbind(c_ans,ans_c)
d_ans$dates<-format(d_ans$dates,"%b %Y")
d_ans
```

